{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-02 Paper/main.tex
Note on the geneartion of similar curves. Has to be more detailed.

>>>>

		 {\color{blue} We should mention how we derived the original principal components. (bspline basis and number of basis functions and harmonics.) As we chose a high number for both to capture all features of the data set. As we explain the approximations for the estimation, this question could come up, so we have to make it specific.}
